\documentclass[11pt]{article}
\newcommand{\numpy}{{\tt numpy}}    % tt font for numpy
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=cyan,
    filecolor=magenta,      
    urlcolor=blue,
}

\begin{document}

\noindent\fbox{%
    \parbox{\dimexpr\linewidth-2\fboxsep-2\fboxrule}{%
    $$\mbox{\Large \textbf {CS 111 (S22): Homework 1}}$$
    $$\mbox{\textbf {Due Monday, April 4th by 11:59 PM}}$$ 
    }%
}
$$\mbox{\textbf {NAME and PERM ID No.:} Gaucho Ol\'e, 1234567 (replace with yours)}$$
$$\mbox{\textbf {UCSB EMAIL:} GauchoOle@ucsb.edu (replace with yours)}$$
$$\mbox{\textbf {Homework Buddy:} ( remove entire line if not applicable)}$$

\medskip

The purpose of this homework assignment is to review some of the math background
for the class, and to help you decide if there is anything you want to 
brush up on. If any of these questions baffles you,
it will be easier to pick up the concept right now than struggle with it
later. Each question is worth 10 points. 

\textbf{PLEASE SHOW ALL YOUR WORK - DON'T JUST WRITE THE ANSWER!}

\begin{enumerate}

\item
Let
$$ A = \left(
\begin{array}{ccc}
3 & -1 & 2 \\ 	
0 & 1 & 2 \\ 
1 & 0 & -1 \\
\end{array} 
\right). $$
What is $A^T$?  What is $A^2$?  What is $A^TA$?
(Do these computations both by hand and with \numpy - and show the code)

\item
The notation $||x||_2$ means the Euclidean norm (also called the 2-norm,
or just the length) of the vector $x$.  
What is $||(3, 1, 4, 1, 5)^T||_2$?

\item
Consider the following system of three equations in three unknowns.
\begin{eqnarray}
 2x_1 - 3x_2 + x_3  & =  & 1 \\
 2x_2 + 3x_3  & =  & 7 \\
 x_1 + x_3  & = & 4 
\end{eqnarray}
First write this system in the form $Ax=b$, 
where $A$ is a matrix and $x$ and $b$ are vectors. 
Second, write two lines of \numpy\ code that use {\tt np.array()} to
create $A$ and $b$ as \numpy\ arrays. 

\item
What vector $x$ solves the system above? Do this one by hand first. Then write the \numpy\ code that solves for $x$. Are your answers \textit{exactly} the same?

\item
Write down a 2-by-2 matrix $A$ and a 2-vector $b$ such that $Ax=b$ has no 
solution.  Explain in a sentence why there are no solutions.

\item
Write down a 2-by-2 matrix $A$ and a 2-vector $b$ such that $Ax=b$ has 
more than one solution.  Give two different solutions.

\item
Recall that a number $\lambda$ is an {\em eigenvalue} 
of a matrix $A$ if there is some vector $x$ 
(an {\em eigenvector}) for which $Ax = \lambda x$.
Give an eigenvalue of the following matrix, and a corresponding eigenvector. Do this by hand only.
$$ A = \left(
\begin{array}{cc}
4 & -1 \\ 	
-1 & 4 \\
\end{array} 
\right). $$

\item
If $f(x)=7x^3-2x^2+4x-5$, what is $f'(x)$, the derivative of $f(x)$?

\item
The height in feet of a bullet fired straight up is
given by $h=1280t-16t^2$, where $t$ is in seconds.
What is the maximum height the bullet will reach? 
When will it hit the ground? Show how you arrived at your answer.

\item
Suppose $y$ is a function of $x$ that satisfies
$dy/dx = xy$, and also suppose $y=1$ when $x=0$.
Write $y$ as a function of $x$.

\end{enumerate}

\end{document}
